\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for\\ Pearson Correlation Coefficient }

### 2021-03-22 Documents/Paper_main/Paper_main.Rnw
pre submission review

Before we proceed, it is worth noting that there are other recent valuable tools that start from different premises for designing and evaluating studies. Among others, we refer the interested reader to methods which start from the definition of a small effect size of interest \parencite[SESOI; for a tutorial, see][]{lakensEquivalenceTestingPsychological2018}.

>>>>

Before we proceed, it is worth noting that there are other recent valuable tools that start from different premises for designing and evaluating studies. Among others, we refer the interested reader to methods which start from the definition of the smallest effect size of interest \parencite[SESOI; for a tutorial, see][]{lakensEquivalenceTestingPsychological2018}.
